### 2017-10-10 paper.tex

The collaborative development methods pioneered by the open source software community
offer a way to create lessons that are open, accessible, and sustainable.
This paper presents ten simple rules for doing this
drawn from our experience with several successful projects.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}

Lessons take significant effort to build and  maintain.
We have found that
the collaborative development methods pioneered by the open source software community
are an effective, economical way to create and sustain lessons
that can be used by large numbers of people in a wide variety of contexts.
The ten simple rules outlined in this paper
summarize the best practices that we have helped evolve
in several successful open education projects aimed at researchers and research librarians
in a wide range of disciplines.

>>>>

Lessons take significant effort to build and maintain.
The collaborative development methods pioneered by the open source software community
offer an effective, economical way to create and sustain lessons
that can be used by large numbers of people in a wide variety of contexts.
The ten simple rules outlined in this paper
summarize the best practices that have been implemented
by several successful open education projects aimed at researchers and research librarians
in a wide range of disciplines.
